---
title: "Assignment_3_Adriana"
author: "Adriana"
date: "2024-02-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eval=FALSE, include=FALSE}
install.packages(c("usethis", "readr"))
install.packages("tidyverse")
```

#Load packages and import majors list from Github
```{r}
library(usethis)
library(tidyverse)
library(readr)
```

```{r}
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"

majors_list <- read.csv(url)
```

##1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
filtered_majors <- subset(majors_list, grepl("DATA|STATISTICS", Major))
```

#2 Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"

into 

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
vector <- c("bell pepper", "billberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
print(vector)
```
# Return :c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
string_with_quotes <- paste0('"', paste(vector, collapse = '","'), '"')
print(string_with_quotes)
```

```{r does this work?}
dput(vector)
```

#3 REGEX Describe, in words, what these expressions will match:
(.)\1\1 

(a) This will match any string that contains three identical characters in a row.

"(.)(.)\\2\\1"

(b) This will match any string that consists of a quotation mark followed by two characters and the literal string \2\1, and a closing quotation mark. The literal string includes \2\1 because there is an escape backslash present. 

(..)\1

(c) I think this will match a string where the first two characters are the same followed by another 2 adjacent repeat characters. The backslash is referring to group 1. 


"(.).\\1.\\1"

(d) This will match any string that consists of a quotation mark followed by any two characters, followed by the literal string \1 and any character, then another literal \1 and ends with a closing quotation mark. 

 "(.)(.)(.).*\\3\\2\\1"
 
(e) This will match any string starting with a quotation mark and consisting of 3(any) or more characters and then the literal string \3\2\1 followed by a closing quotation mark.

#4 Construct regular expressions to match words that:

(a) Start and end with the same character.:
^(.)\.*\1$

+ ^ and $: Asserts the start and the end of the string, respectively.
+ (.): Captures any single character (the parenthesis make it a group.)
+ .*: Matches zero or more word characters (letters, digits, or underscores).Could also be a \w instead
+ \1: Back reference to the first capturing group.

(b) Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.):
(.)(.).*\1\2

+ (.)(.): captures any two adjacent characters. Note for self: It's not (..) because the letters don't have to be the same
+ .*: any characters in between
+ \1\2: back references to the first two capturing groups, ensuring that what will be returned is any string that repeats a pair of adjacent characters and any characters in between.

(c) Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.):
(.).*\1.*\1

+ (.): captures any single character, could also be \w for a single word char.
+ .*: represents anything in between
+ \1: references back to the first group(any single character) and it's in here twice to match any repeats that occur at least 3 times
